Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-08-24 manu-draft.qmd
added refs about seagrass disease

Other areas showing seagrass loss - Florida Bay is different, less water flowing out of everglad and compounding SLR has elevated salinity and likely stress in other direction. Also, Biscayne Bay and IRL is a lot like OTB, poor flushing for example.

>>>>

Other areas showing seagrass loss - Florida Bay is different, less water flowing out of everglades and compounding SLR has elevated salinity and likely stress in other direction. Also, Biscayne Bay and IRL is a lot like OTB, poor flushing for example.

Viral/disease effects on seagrass change, [@vanbogaert2018] for TB and [@duffin2021] for Florida Bay.
